Drug sensitivity prediction with the normal inverse Gaussian prior informed by external data

### 2019-11-25 docs/manuscript1.Rnw
changed manuscript1.Rnw

>>>>

est1 <- cbind(fit[, 1], c(NA, 0, 0, NA, 0), fit[, 2])
colnames(est1) <- c("intercept", "not in pathway", "in pathway")
est2 <- cbind(fit[, 3:5], c(NA, 0, NA, 0, NA), fit[, c(7:6)], 
              c(NA, 0, NA, 0, NA))
colnames(est2) <- c("intercept", "experimental", "development", "approved",
                    "unkown", "targeted", "cytotoxic")
